\documentclass[a4paper, 12pt]{article}
\begin{document}
\vspace*{8pt}
\subsection{{University of Arizona}}
\subtext{{Astronomy Education for Undergraduate Majors}\hfill Nov 2024 - Present}
\begin{zitemize}
    \item Designed a lesson plan utilizing Jupyter Notebooks to teach basic programming concepts along with improving students astronomy knowledge
    \item This is a work in progress and all educational materials will be made publicly available
\end{zitemize}

\vspace*{5pt}
\subtext{{Space Drafts Organizer} \hfill Nov 2024 - Present}
\begin{zitemize}
    \item Facilitate monthly public science talks in Tucson, AZ as part of the international organization Astronomy on TAP
\end{zitemize}

\vspace*{5pt}
\subtext{{Black Hole Summer Camp Science Expert} \hfill June 2024}
\begin{zitemize}
    \item Teach elementary school students about Black Holes as part of the Flandrau Science Center Black Hole Summer Camp.
    \item Collaborate with an elementary school instructor to create interactive teaching activities on Black Holes.
\end{zitemize}

\vspace*{8pt}
\subsection {{Siena College}}
\subtext{{Teaching Assistant}\hfill Aug 2020 - May 2023}
\begin{zitemize}
\item Facilitated a lab or office hours to help students learn physics, programming, and data science concepts.
\item Classes include Introduction to Exploratory Data Analysis and Visualization, Computational Physics, General Physics I, \& General Physics II.
\end{zitemize}

\vspace*{5pt}
\subtext{{Peer Tutor}\hfill Aug 2020 - May 2022}
\begin{zitemize}
\item Explained difficult academic concepts to peers taking General Physics.
\end{zitemize}

\vspace*{5pt}
\subtext{{Physics Club Outreach} \hfill Feb 2020, Oct 2022, Apr 2023}
\begin{zitemize}
    \item Taught middle school aged students basic physics and engineering concepts.
\end{zitemize}

\vspace*{5pt}
\subtext{Siena College Public Observing Night \hfill Sep 2022 - May 2023}
\begin{zitemize}
    \item Telescope operator for Siena College public observing nights.
    \item Taught other students about the astronomical objects being observed. 
\end{zitemize}
\vspace*{5pt}

\end{document}